---
title: "Class Survey"
author: "Gloria Hernandez"
date: "10/23/2018"
output:
  html_document:
    df_print: paged
---


```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)

```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->
  
We start by loading the data into 2 data frames

```{r}
library(readr)
Sec02 <- read_csv("Class_Survey_Sec02.csv")
Sec23 <- read_csv("Class_Survey_Sec23.csv")
Sec02 <- mutate(Sec02,sect="PM")
Sec23 <- mutate(Sec23,sect="Eve")
alldat <- bind_rows(Sec02,Sec23)
```

```{r}
write.csv(x=alldat,file="alldat.csv")
```

```{r}
dataset <- 
  read.table("D:/Project_folders/Class_Survey/alldat.csv", 
  header=TRUE, sep=",", na.strings="NA", dec=".", 
  strip.white=TRUE)

```

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->
  
  We have put together the two data sets from the pm and evening classes into a dataset called alldat.We use that data to answer our questions.There are approx 40 responses in each data set and 83 overall. We load the data from the commander, use boxplots to visualize group differences and use the t test to determine whether the means of two groups are equal to each other.   

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
Boxplot(Age_yrs~sect, data=alldat, id=list(method="y"))

```
  
 The boxplot that the range of the guys time up and down is more compact than the girls average time. The upper whisker of the guys boxplot ends roughly after the girls median is initiated.
 
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->
  
```{r}
numSummary(alldat[,"Age_yrs", drop=FALSE], 
  groups=alldat$sect, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```
  
 The standard deviation shows that the ages in the PM class are closer together than the ages in the EVE class. The average of the EVE class is greater than the average of the PM class.    
  
```{r}
numSummary(dataset[,"time_down_up", drop=FALSE], 
  groups=dataset$Gender, statistics=c("mean", "sd", "IQR", 
  "quantiles"), quantiles=c(0,.25,.5,.75,1))
```
  
  The mean of the girls time is 30.64286. The mean of the guys time is 24.05000. On average the girls took about 6.6 seconds longer going up and down the stairs than the guys.   

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->
  
```{r}
t.test(Age_yrs~sect, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=alldat)
```
  
  This shows that the average of the evening class is higher than the PM class. The p value is 0.009678, which is very low therefore we can reject the null hypothesis. 
  

  
```{r}
t.test(time_down_up~Gender, alternative='two.sided', 
  conf.level=.95, var.equal=FALSE, data=dataset)
```
  
  The t test is used to determine whether the means of the two groups are equal to each other. As a result, the difference was  6.592857. The p value is 0.01116 which again is very low therefore we can reject the null hypothesis. 
  
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
After reviewing the results numerically, graphically and using the t test, we can conclude that the students in the evening class are older than the students in the afternoon class. Results also showed that the average time down and up the stairs is not the same for guys and girls. Furthermore results also show not only were they different but that the guys had significantly faster times. The p values from the t test were very low therefore we can reject the null hypothesis and accept the  alternative hypothesis in which the times between the guys and girls were significantly different.  

